Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/two_photon_thermionic/two_photon_thermionic.tex
fix binning factor of two in 2PTE plot
began tweaking 2PTE section

\section{Two-photon Assisted Thermionic Photoemission} \label{sec:two_photon_thermionic}

>>>>

\section{Two-photon Assisted Thermionic Emission} \label{sec:two_photon_thermionic}

Although single-photon photoemission is more efficient than multi-photon photoemission, the concept remains the same; an electron in the photocathode must absorb enough energy to exceed the vacuum level.
In multi-photon photoemission this energy is attained by absorbing multiple photons.
As this is more likely to occur when more photons are present, the efficiency, and thus the yield, is proportional to the laser intensity to the power of the number of photons required.
Two-photon photoemission, therefore, will have yield that is quadratic in laser intensity ($I^2$).

Two-photon assisted thermionic emission (2PTE) occurs when two photons provide nearly enough energy to emit a cold electron, and therefore a hotter electron, in the tail of the Fermi distribution, may have enough energy to be emitted \cite{yen_thermally_1980}.
Of course this is even less efficient than two-photon photoemission, but as three-photon photoemission goes as $I^3$, 2PTE will still be the dominant photoemission mechanism.
For thermionic emission from electrons at a temperature $T_e$, the rms transverse momentum $\Delta p_{\smallT}$ is given by 
\begin{equation}
  \Delta p_{\smallT} = \sqrt{m k_B T_e} \,\text{,}
\end{equation}
where $k_B$ is the Boltzmann constant \cite{dowell_quantum_2009,jensen_emittance_2010}.
Since a high laser intensity is required to drive 2PTE, the laser itself will heat the electrons, therefore we expect the measured Fourier plane spot size to grow as the square root of the laser pulse energy.
